\section{Objective}
\label{sec:objective}
\subsection{Main Objective Statement}
The primary objective of this project is to design, develop, and deploy an emotional wellness robot capable of recognizing and responding to stress and anxiety symptoms in users through the integration of AI technologies such as facial emotion recognition and speech emotion recognition. The robot must fulfill all three key pillars of customer expectations in emotional wellness robots: design, interactivity, and empathy.


\subsection{Specific Goals}
\begin{itemize}
    \item Design intuitive appearance and interactive features for the robot with expert supervision from Chula Student Wellness (CUSW).
    \item Develop an accurate emotion detection algorithm that captures the user’s emotional state, leveraging software design principles taught throughout the curriculum.
    \item Develop empathetic human-robot interactions that promote emotional wellness within the customer, leveraging various engineering design principles taught throughout the curriculum.
    \item Conduct extensive testing and refinement based on user feedback.
\end{itemize}
    
\subsection{Measurable Outcomes}
\begin{itemize}
    \item Achieve a relative reduction in self-reported anxiety among tested users.
    \item Achieve a benchmark in accuracy metrics for emotion detection.
    \item Obtain an improved before-and-after positivity score among tested users.
\end{itemize}

\subsection{Relevance or Significance}
With “Terror Outbursts” being one of the major societal challenges in Thailand, there is a pressing need
for accessible positivity promotion. Our robot aims to bridge the gap between traditional therapy sessions
by providing immediate support to individuals struggling with anxiety
