\section{Key Learnings}
This section highlights the most important lessons learned throughout the course of the project. While a few project objectives remained unfulfilled, each challenge presented a valuable opportunity for reflection, growth, and improvement.

\begin{itemize}
    \item \textbf{\textit{Effective time management.}} Although the team initially established a detailed implementation timeline for each MVP stage—outlining weekly objectives and milestones—unforeseen technical issues and delays in decision-making often pushed the project off track. This experience emphasized the need to build in buffer periods and adopt more flexible, iterative planning approaches.
    \item \textbf{\textit{Prioritize analysis before implementation.}} In some cases, hardware components were selected and integrated before thorough calculations—such as torque requirements or load-bearing capacity—were conducted. This led to design inefficiencies and the need for costly rework. Going forward, the team recognizes the value of rigorous pre-implementation analysis to ensure optimal system performance and reduce trial-and-error.
    \item \textbf{\textit{Engaging end users early enhances design relevance.}} As the project progressed, it became evident that involving users—especially those within the target demographic—earlier in the process would have provided clearer insights into their needs and expectations. By integrating user feedback more consistently throughout the development cycle, the team could have made more informed design decisions, leading to a more intuitive and emotionally resonant final product. 
    \item \textbf{\textit{Prototyping early, even imperfectly, accelerates progress.}} At times, the team hesitated to build early prototypes due to incomplete specifications or concerns about quality. However, we learned that early prototyping—even with placeholder components—helps uncover design flaws, integration issues, and user experience challenges much sooner. These quick iterations saved significant time and resources that would have otherwise been spent refining ideas that were ultimately unfeasible.
\end{itemize}