\section{Team Roles and Responsibilities}

Although each student is assigned a specific component of the project, it is important to recognize that we will collaborate on various aspects. As a result, each role may evolve and shift as the project progresses.
\begin{enumerate}
    \item{\textbf{Kridbhume Chammanard - Project Manager}}
    
    As the Project Manager, Kridbhume Chammanard is responsible for overseeing the entire project, ensuring that all activities align with the established goals and deadlines. Kridbhume will delegate tasks to the project engineers, manage the project timeline, and make necessary adjustments to keep the project on track. Engaging with advisors from ISE and Chula Student Wellness is a key aspect of the role, including providing regular updates and consultations. Kridbhume will streamline the work processes for the project engineers to enhance efficiency and productivity, and will also professionally review and approve all deliverables before submission. Additionally, Kridbhume will oversee the overall project budget, ensuring that expenditures are within allocated limits and that resources are used effectively.
    
    \item{\textbf{Thitaya Divari - Project Engineer, Product Development}}
    
    Thitaya Divari, as the Project Engineer for Product Development, will focus on designing the user experience (UX) of the robot, utilizing CAD software to develop and refine user interfaces. Thitaya will be responsible for sourcing and gathering all necessary hardware components required for the robot’s physical construction, as well as working on the assembly and testing of these components to ensure they meet design specifications. Managing the budget allocated for hardware components and product development activities will be another critical responsibility, including tracking expenses and making adjustments as needed. Thitaya will also prepare detailed documentation of the product development process, including design specifications, component lists, and testing results.
    
    \item{\textbf{Tibet Buramarn - Project Engineer, Software Development}}
    
    In the role of Project Engineer for Software Development, Tibet Buramarn will lead all software development initiatives, including coding, testing, and integrating the robot’s software functionalities. Tibet will implement and manage DevOps practices within the project, ensuring smooth development, deployment, and maintenance of the software. A significant aspect of the role includes ensuring seamless integration of software with hardware components, addressing any compatibility issues, and optimizing performance. Tibet will conduct thorough testing and debugging of the software to identify and resolve issues, ensuring the reliability and functionality of the system.
\end{enumerate}
    