\section{Objective}

\subsection{Main Objective Statement}
The primary objective of this project is to design, develop, and deploy an emotional wellness robot
capable of recognizing and responding to stress and anxiety symptoms in users through the integration of
AI technologies such as computer vision and natural language processing. The robot must fulfill all three
key pillars of customer expectations in emotional wellness robots: design, interactivity, and empathy.

\subsection{Specific Goals}
\begin{itemize}
    \item Design an anthropomorphic robotic outer shell that resonates with the target customer segment.
    \item Design interactive verbal and non-verbal features for the robot, such as reaction when the user smiles, with expert supervision from Chula Student Wellness (CUSW).
    \item Develop an accurate emotion detection algorithm that captures the user’s state of stress through speech emotion recognition and facial expression recognition.
    \item Develop empathetic human-robot interactions that promote emotional wellness within the customer.
    \item Conduct extensive testing and refinement based on user feedback.
\end{itemize}

\subsection{Measurable Outcomes}
\begin{itemize}
    \item Perform end user testing in at least 3 users for 7 days each
    \item Obtain a reduction in self-reported anxiety score after using the robot (e,g Self-reported anxiety score before using Pookie is 7, but after using Pookie it becomes 6)
    \item Obtain an increase in self-reported positivity score after using the robot (e,g Self-reported positivity score before using Pookie is 7, but after using Pookie it becomes 8)
    \item Achieve a benchmark in accuracy metrics for emotion detection.
\end{itemize}

\subsection{Relevance or Significance}
With “Terror Outbursts” being one of the major societal challenges in Thailand, there is a pressing need
for accessible positivity promotion. Our robot aims to bridge the gap between traditional therapy sessions
by providing immediate support to individuals struggling with anxiety
