\section{Objective}

\subsection{Main Objective Statement}
The primary objective of this project is to design, develop, and deploy an emotional wellness robot capable of recognizing and responding to stress and anxiety symptoms in users through the integration of AI technologies such as computer vision and natural language processing. The robot must fulfill all three key pillars of customer expectations in emotional wellness robots: design, interactivity, and empathy.

\subsection{Specific Goals}
\begin{itemize}
    \item Design an anthropomorphic robotic outer shell that resonates with the target customer segment.
    \item Design interactive verbal and non-verbal features for the robot, such as making sounds when the robot is touched on the head, with expert supervision from Chula Student Wellness (CUSW).
    \item Develop an accurate emotion detection algorithm that captures the user’s state of anxiety through speech emotion recognition and facial expression recognition.
    \item Develop empathetic human-robot interactions that promote emotional wellness within the customer.
    \item Finalize a customer-centric design obtained through market validation efforts.
    \item Conduct extensive testing and refinement based on user feedback.
\end{itemize}

\subsection{Measurable Outcomes}
\begin{itemize}
    \item Achieve a relative reduction in self-reported anxiety.
    \item Achieve a benchmark in accuracy metrics for emotion detection.
    \item Obtain an improved before-and-after positivity score.
\end{itemize}

\subsection{Relevance or Significance}
With “Terror Outbursts” being one of the major societal challenges in Thailand, there is a pressing need for accessible positivity promotion. Our robot aims to bridge the gap between traditional therapy sessions by providing immediate support to individuals struggling with anxiety.